\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage[letterpaper, portrait, margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{graphicx}

\usepackage{hyperref}
\hypersetup{
colorlinks=true,
    linkcolor=black,
    filecolor=black,      
    urlcolor=blue,
    citecolor=black,
}
\usepackage{natbib}

\usepackage{titlesec}
  
\title{Homework 5}
\author{Ryan Ellis}
\date{Spring semester 2023}
  
\begin{document}
  
\maketitle

\section{Python}
\subsection{}
\begin{itemize}
    \item The coefficient on the endogenous $mpg$ is -22.21. A unit increase in $mpg$ corresponds to a decrease in price of \$22.21.
\end{itemize}

\subsection{}
\begin{itemize}
    \item We should be concerned primarily with omitted variable bias, or equivalently, the possibility that $mpg$ is a confounder correlated with both $price$ and the error term. It's unlikely that we have measurement error or simultaneity in this particular application.
\end{itemize}

\subsection{}
\input{homework5/output/my_table.tex}

\clearpage

\subsection{}
\begin{itemize}
    \item Using GMM, the second-stage coefficient of interest ($mpg$) is 150.43, with S.E. 63.05. The point estimate is identical to treatment (1) in the table above, but with slightly larger errors, likely due to a suboptimal weighting matrix in the GMM estimation. GMM is more efficient than 2SLS when there are multiple instruments. In this case, there is only one.
\end{itemize}


\section{Stata}

\subsection{}
\input{homework5/output/liml.tex} \centering

\subsection{}
\begin{itemize}
    \item The MOP effective F-statistic is 78.362. The 5\% critical value is 37.418, so we reject the null hypothesis (that $weight$ is a weak instrument).
\end{itemize}
\end{document}